Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-07 paper/main.tex
Updates

We analyzed the performance of \textit{ExpertInLoop} algorithm by comparing it
with three commonly used automated algorithms: PC, Hill-Climb Search, and
Greedy Equivalence Search (GES). For the analysis, we simulated data from known
DAG structures and

>>>>

We analyzed the performance of \textit{ExpertInLoop} algorithm by comparing it
with three other automated algorithms: PC, Hill-Climb Search, and Greedy
Equivalence Search (GES). For the analysis, we simulated data from known DAG
structures and use the algorithms to recover the original DAG. We start by
generating a random DAG on $10$ nodes and use linear models with random effects
to generate the data. We vary the edge probability of the DAG to generate DAGs
with varying density. We repeat the data generation $30$ times for each density
value for the DAG. We compare the learned DAG to the original DAG using two
metrics: Structural Hamming Distance (SHD) and Structural Intervention Distance
(SID) \citep{Peters2015}.

As both PC and Hill-Climb Search can only give us a CPDAG, we
